### 2021-11-03 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@40a6ba0ece7ab414b8f3153607c43069d1b9edb6 🚀

\begin{enumerate}
    \itemDespite their importance in many ecological processes,
collecting data and information on ecological interactions is an
exceedingly challenging task. For this reason, large parts of the world
have a data deficit when it comes to species interactions, and how the
resulting networks are structured. As data collection alone is unlikely
to be sufficient, community ecologists must adopt predictive methods.%
    \itemWe present a methodological framework that uses graph embedding
and transfer learning to assemble a predicted list of trophic
interactions of a species pool for which their interactions are unknown.
Specifically, we `learn' the information from a known interaction
network by inferring the latent traits of species and infer the latent
traits of a species pool for which we have no \emph{a priori}
interaction data based on their phylogenetic relatedness to species from
the known network. The latent traits can then be used to predict
interactions and construct and interaction network.%
    \itemHere we assembled a metaweb for Canadian mammals derived from
interactions in the European food web, despite only 4\% of common
species being shared between the two locations. The results of the
predictive model are compared against databases of recorded pairwise
interactions, showing that we correctly recover 91\% of known
interactions.%
    \itemThe framework itself is robust even when the known network is
incomplete or contains spurious interactions making it an ideal
candidate as a tool for filling gaps when it comes to species
interactions. We provide guidance on how this frameworl can be adapted
by substituting some approaches or predictors in order to make it more
generally applicable.%
\end{enumerate}

>>>>

\begin{enumerate}
    \item Despite their importance in many ecological processes,
collecting data and information on ecological interactions is an
exceedingly challenging task. For this reason, large parts of the world
have a data deficit when it comes to species interactions, and how the
resulting networks are structured. As data collection alone is unlikely
to be sufficient, community ecologists must adopt predictive methods.%
    \item We present a methodological framework that uses graph
embedding and transfer learning to assemble a predicted list of trophic
interactions of a species pool for which their interactions are unknown.
Specifically, we `learn' the information from a known interaction
network by inferring the latent traits of species and infer the latent
traits of a species pool for which we have no \emph{a priori}
interaction data based on their phylogenetic relatedness to species from
the known network. The latent traits can then be used to predict
interactions and construct and interaction network.%
    \item Here we assembled a metaweb for Canadian mammals derived from
interactions in the European food web, despite only 4\% of common
species being shared between the two locations. The results of the
predictive model are compared against databases of recorded pairwise
interactions, showing that we correctly recover 91\% of known
interactions.%
    \item The framework itself is robust even when the known network is
incomplete or contains spurious interactions making it an ideal
candidate as a tool for filling gaps when it comes to species
interactions. We provide guidance on how this frameworl can be adapted
by substituting some approaches or predictors in order to make it more
generally applicable.%
\end{enumerate}
